---
title: "Case_study"
author: "Xue Yang"
date: "10/9/2018"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_bw() + theme(legend.position = "bottom"))
```

## Load the data

```{r}
library(p8105.datasets)
data(nyc_airbnb)
```


## View the data

```{r}
nyc_airbnb
```

## Rename/clean some things

```{r}
nyc_airbnb = 
  nyc_airbnb %>%
  mutate(stars = review_scores_location / 2) %>% 
  rename(boro = neighbourhood_group) 
```

```{r}
nyc_airbnb %>% 
  count(boro)

nyc_airbnb %>% 
  count(boro, neighbourhood)
```


## Some questions

* Does rating vary by neighborhood, room type, or both?
* How is price related to other variables?
* Where are rentals located?
* What's the most expensive area? What about the least?
* Which listing have the most unfilled days?
* Which area has the highest density of listings?
* What are some host characteristics? How many listing? What's asociated with rating?


## Some answers

#### Does rating vary by neighborhood, room type, or both?

```{r}
nyc_airbnb %>%
  group_by(neighbourhood) %>%
  summarize(median(stars, na.rm = TRUE))

nyc_airbnb %>%
  group_by(room_type) %>%
  summarize(median(stars, na.rm = TRUE),
            n = n()) 
```

```{r}
nyc_airbnb %>%
  group_by(boro, room_type) %>%
  summarize(
     mean(stars, na.rm = TRUE)) 


nyc_airbnb %>%
  group_by(boro, room_type) %>%
  summarize(mean_stars = mean(stars, na.rm = TRUE)) %>%
  spread(key = room_type, value = mean_stars)
  
```


```{r}
ggplot(nyc_airbnb, aes(x = stars), color = boro) +
  geom_histogram() +
  facet_grid(~boro)
```

```{r}
ggplot(nyc_airbnb, aes(x = stars), color = boro) +
  geom_histogram() +
  facet_grid(~room_type)
```


#### Where are rentals located?

```{r}
nyc_airbnb %>% 
  ggplot(aes(x = longitude, y = latitude, color = boro)) +
  geom_point(alpha = .2) +
  facet_grid(~room_type)
  viridis::scale_color_viridis(discrete = TRUE)
```

```{r}
nyc_airbnb %>% 
  filter(boro == "Manhattan") %>% 
  ggplot(aes(x = longitude, y = latitude, color = boro)) +
  geom_point(alpha = .2) +
  facet_grid(~room_type)
  viridis::scale_color_viridis(discrete = TRUE)
```

```{r}
nyc_airbnb %>% 
  filter(boro == "Manhattan",
         price > 1000) %>% 
  ggplot(aes(x = longitude, y = latitude, color = boro)) +
  geom_point(alpha = .2) +
  facet_grid(~room_type)
  viridis::scale_color_viridis(discrete = TRUE)
```

```{r}
nyc_airbnb %>% 
  ggplot(aes(x = longitude, y = latitude, color = price)) +
  geom_point(alpha = .2) +
  facet_grid(~room_type) +
  viridis::scale_color_viridis()
```


#### Expensive areas

```{r}
nyc_airbnb %>%
  select(boro, neighbourhood, price) %>%
  filter(boro == "Brooklyn") %>%
  group_by(neighbourhood) %>%
  summarize(n_listings= n(),
            mean_price = mean(price, na.rm = TRUE),
            median_price = median(price, na.rm = TRUE),
            ) %>%
  top_n(5) 

nyc_airbnb %>%
  select(boro, neighbourhood, price) %>%
  filter(boro == "Manhattan") %>%
  group_by(neighbourhood) %>%
  summarize(n_listings= n(),
            mean_price = mean(price, na.rm = TRUE),
            median_price = median(price, na.rm = TRUE),
            ) %>%
  top_n(5) 

nyc_airbnb %>%
  select(boro, neighbourhood, price) %>%
  filter(boro == "Manhattan") %>%
  group_by(neighbourhood) %>%
  summarize(n_listings= n(),
            mean_price = mean(price, na.rm = TRUE),
            median_price = median(price, na.rm = TRUE),
            ) %>%
  arrange(mean_price) 

nyc_airbnb %>%
  select(boro, neighbourhood, price) %>%
  filter(boro == "Brooklyn") %>%
  group_by(neighbourhood) %>%
  summarize(mean_price = mean(price, na.rm = TRUE),
            median_price = median(price, na.rm = TRUE)) %>%
  top_n(-5) 
```

